CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2024-01-08 paper.Rmd
PFU database --> CL-PFU database
Remove references to repository DOI.

We created a suite of open-source `R` packages 
and the metapackage [CLPFUDatabase][link-clpfudatabase] [@Heun-CLPFUDatabase:2023]
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for 
"Country-Level Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Marshall:2023aa; @Brockway:2024aa].

@@

Input data for the PFU database can be found in @Marshall:2023aa.
Access to the full CL-PFU database can be obtained via correspondence 
with author [P.E.B.](mailto:P.E.Brockway@leeds.ac.uk)^[Because the CL-PFU database contains
primary and final energy [IEA EWEB][link-ieaeweb] data, 
use of the CL-PFU database
is restricted to those who have access to [IEA][link-iea] [EWEB][link-ieaeweb] data.].
If desired, researchers with access to the 
[IEA][link-iea]'s [EWEB][link-ieaeweb] 
data can create their own CL-PFU database 
following the example below.

>>>>

We created a suite of open-source `R` packages 
and the metapackage [CLPFUDatabase][link-clpfudatabase] [@Heun-CLPFUDatabase:2023]
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for 
"Country-Level Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Brockway:2024aa].

@@

Example input data for the CL-PFU database 
(for two countries and two years) 
can be found in the GitHub repository for this paper.
Access to the full CL-PFU database can be obtained via correspondence 
with author [P.E.B.](mailto:P.E.Brockway@leeds.ac.uk)^[Because the CL-PFU database contains
primary and final energy [IEA EWEB][link-ieaeweb] data, 
use of the CL-PFU database
is restricted to those who have access to [IEA][link-iea] [EWEB][link-ieaeweb] data.].
If desired, researchers with access to the 
[IEA][link-iea]'s [EWEB][link-ieaeweb] 
data can create their own CL-PFU database 
following the example below.
